%% ============================================================================
%%  Calibrated Posterior WCE Localization at a Four-Receiver MICS/MedRadio Budget
%%  Full-wave CST simulation study.
%% ============================================================================
\documentclass[journal]{IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{multirow}
\usepackage{array}
\usepackage[hidelinks]{hyperref}

\sisetup{detect-weight=true,detect-family=true}

\title{A Calibrated Posterior for Wireless Capsule Endoscope Localization at a
Four-Receiver MICS/MedRadio Budget: A Full-Wave Simulation Study}

\author{Subramaniam~S.~Murugesan,
Muhammad~Qamar,
Kamil~Yavuz~Kapusuz,
Mohamed~A.~Thaha,
and~Akram~Alomainy
\thanks{S.~S.~Murugesan, M.~Qamar, and A.~Alomainy are with the School of
Electronic Engineering and Computer Science, Queen Mary University of London,
London, U.K. (e-mail: \{s.subramanianmurugesan, m.qamar,
a.alomainy\}@qmul.ac.uk).}%
\thanks{K.~Y.~Kapusuz is with the Department of Information Technology,
IDLab/EM Group, Ghent University/imec, Ghent, Belgium
(e-mail: kamilyavuz.kapusuz@ugent.be).}%
\thanks{M.~A.~Thaha is with the Department of Colorectal Surgery, Royal London
Hospital, Barts Health NHS Trust, London, U.K., and with the Blizard Institute,
National Bowel Research Centre, Barts and the London School of Medicine \&
Dentistry, Queen Mary University of London, London, U.K.
(e-mail: m.a.thaha@qmul.ac.uk).}%
\thanks{This is a full-wave electromagnetic (CST) simulation study; no
measured-phantom or in-vivo results are reported.}}

\begin{document}
\maketitle

\begin{abstract}
\textbf{This is a full-wave electromagnetic CST Studio Suite (CST) simulation
study; we report no measured-phantom or in-vivo results.} We study wireless
capsule endoscope (WCE) localization at a four-receiver budget relevant to the
Medical Implant Communication Service (MICS)/MedRadio band
(\SIrange{401}{406}{MHz}). We ask whether such a system can report calibrated
confidence in capsule position, not only a point estimate. Full-wave channels
are simulated over a \SIrange{380}{430}{MHz} sweep; strict-legal-band evidence is
the single-tone magnitude-only ablation. On a corrected cuboid phantom geometry
(receivers on the $\pm x/\pm z$ vertical walls, no $y$-face coverage) and a
strictly position-grouped 5-fold cross-validation protocol, we benchmark a
conditional flow-matching (CFM) posterior against a deterministic regression
backbone, probabilistic baselines (deep ensemble, MC-dropout, mixture density
networks, split conformal), and ten classical regressors. Beyond point accuracy,
the CFM posterior is calibrated: its marginal 50/90/95\% coverages track the
nominal levels ($0.766/0.935/0.944$ on the held-out initial-stage subset,
$N=1980$; $0.832/0.970/0.975$ when all combined-set positions are scored by the
CFM alone), and its predicted spread ranks actual error (Spearman
$\rho\approx0.60$). Point accuracy is within \SI{0.014}{cm} of the deterministic
backbone (\SI{0.354}{cm} vs \SI{0.340}{cm} 3D MAE on the combined $N=3935$ set).
A controlled mirror-symmetric array ablation further indicates, on this
controlled geometry, that posterior modality tracks forward-operator
invertibility: the CFM posterior is bimodal when the ablation array makes $y$
unobservable and unimodal on the main anti-symmetric side-wall array. The same
posterior width carries the orientation-induced uncertainty measured across five
axis-aligned capsule poses ($\rho\approx0.85$). A feature-deployability ablation
locates the single-tone, magnitude-only floor at ${\sim}\SI{1.5}{cm}$ and shows
that the sub-centimetre regime requires phase-coherent receivers. \textbf{We
make no claim to state-of-the-art point accuracy}: at the four-receiver
MICS/MedRadio budget, real-phantom systems are more accurate, and we declare the
simulation-vs-real and frequency-band confounds explicitly. To our knowledge,
this is the first flow-matching/generative WCE-RF position posterior with
empirical multi-level coverage under position-grouped cross-validation.
\end{abstract}

\begin{IEEEkeywords}
Wireless capsule endoscopy, RF localization, uncertainty quantification,
calibration, conformal prediction, conditional flow matching, generative
posterior, MICS/MedRadio band, simulation-based inference.
\end{IEEEkeywords}

\input{sections/intro}
\input{sections/related}
\input{sections/dataset}
\input{sections/method}
\input{sections/results}
\input{sections/discussion}
\input{sections/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{refs}

\end{document}
